Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber{}}}

### 2018-02-08 Paper.tex
R_{\mathrm{b}} as the block reward => R_{\mathrm{block}} + links

\begin{enumerate}
\item Validate (or, if mining, determine) ommers;
\item validate (or, if mining, determine) transactions;
\item apply rewards;
\item verify (or, if mining, compute a valid) state and \hyperlink{block nonce}{block nonce}.
\end{enumerate}

@@

The validation of \hyperlink{ommer_block_headers_B__U}{ommer headers} means nothing more than verifying that each ommer header is both a valid header and satisfies the relation of $N$th-generation ommer to the present block where $N \leq 6$. The maximum of ommer headers is two. Formally:
\begin{equation}
\lVert B_{\mathbf{U}} \rVert \leqslant 2 \bigwedge_{\mathbf{U} \in B_{\mathbf{U}}} \hyperlink{block_header_validity_function}{V({\mathbf{U}}})\; \wedge \; k({\mathbf{U}}, P(\mathbf{B}_{\mathbf{H}})_{\mathbf{H}}, 6)
\end{equation}

@@

The application of rewards to a block involves raising the balance of the accounts of the beneficiary address of the block and each ommer by a certain amount. We raise the block's beneficiary account by $R_{\mathrm{b}}$; for each ommer, we raise the block's beneficiary by an additional $\frac{1}{32}$ of the block reward and the beneficiary of the ommer gets rewarded depending on the block number.\hypertarget{Omega}{} Formally we define the function $\Omega$:
\begin{eqnarray}
\\ \nonumber
\Omega(B, \boldsymbol{\sigma}) & \equiv & \boldsymbol{\sigma}': \boldsymbol{\sigma}' = \boldsymbol{\sigma} \quad \text{except:} \\
\qquad\boldsymbol{\sigma}'[{\mathbf{B}_{H}}_{\mathrm{c}}]_{\mathrm{b}} & = & \boldsymbol{\sigma}[{\mathbf{B}_{H}}_{\mathrm{c}}]_{\mathrm{b}} + (1 + \frac{\lVert \mathbf{B}_{\mathbf{U}}\rVert}{32})R_{\mathrm{b}} \\
\qquad\forall_{\mathbf{U} \in \mathbf{B}_{\mathbf{U}}}: \\ \nonumber
\boldsymbol{\sigma}'[\mathbf{U}_{\mathrm{c}}] & = & \begin{cases}
\varnothing &\text{if}\ \boldsymbol{\sigma}[\mathbf{U}_{\mathrm{c}}] = \varnothing\ \wedge\ R = 0 \\
\mathbf{a}' &\text{otherwise}
\end{cases} \\
\mathbf{a}' &\equiv& (\boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathrm{n}}, \boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathrm{b}} + R, \boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathbf{s}}, \boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathrm{c}}) \\
R & \equiv & (1 + \frac{1}{8} (U_{\mathrm{i}} - {B_{H}}_{\mathrm{i}})) R_{\mathrm{b}}
\end{eqnarray}

@@

\hypertarget{block_reward_R__b}{}We define the block reward as 3 Ether:
\begin{equation}
\text{Let} \quad R_{\mathrm{b}} = 3 \times 10^{18}
\end{equation}

@@

\hypertarget{RLP_serialisation_of_a_byte_array_R__b_word_def}{}If the value to be serialised is a byte-array, the RLP serialisation takes one of three forms:

@@

\hypertarget{RLP_serialisation_of_a_byte_array_R__b_math_def}{}Formally, we define $R_{\mathrm{b}}$:
\begin{eqnarray}
R_{\mathrm{b}}(\mathbf{x}) & \equiv & \begin{cases}
\mathbf{x} & \text{if} \quad \lVert \mathbf{x} \rVert = 1 \wedge \mathbf{x}[0] < 128 \\
(128 + \lVert \mathbf{x} \rVert) \cdot \mathbf{x} & \text{else if} \quad \lVert \mathbf{x} \rVert < 56 \\
\big(183 + \big\lVert \mathtt{\tiny BE}(\lVert \mathbf{x} \rVert) \big\rVert \big) \cdot \mathtt{\tiny BE}(\lVert \mathbf{x} \rVert) \cdot \mathbf{x} & \text{otherwise}
\end{cases} \\
\mathtt{\tiny BE}(x) & \equiv & (b_0, b_1, ...): b_0 \neq 0 \wedge x = \sum_{n = 0}^{n < \lVert \mathbf{b} \rVert} b_{\mathrm{n}} \cdot 256^{\lVert \mathbf{b} \rVert - 1 - n} \\
(a) \cdot (b, c) \cdot (d, e) & = & (a, b, c, d, e)
\end{eqnarray}

@@

\hypertarget{RLP_serialisation_of_a_sequence_of_other_items_R__l_word_def}{}If instead, the value to be serialised is a sequence of other items then the RLP serialisation takes one of two forms:

>>>>

\begin{enumerate}
\item Validate (or, if mining, determine) ommers;
\item validate (or, if mining, determine) transactions;
\item apply rewards;
\item verify (or, if mining, compute a valid) state and nonce.
\end{enumerate}

@@

The validation of ommer headers means nothing more than verifying that each ommer header is both a valid header and satisfies the relation of $N$th-generation ommer to the present block where $N \leq 6$. The maximum of ommer headers is two. Formally:
\begin{equation}
\lVert B_{\mathbf{U}} \rVert \leqslant 2 \bigwedge_{\mathbf{U} \in B_{\mathbf{U}}} V({\mathbf{U}}) \; \wedge \; k({\mathbf{U}}, P(\mathbf{B}_{\mathbf{H}})_{\mathbf{H}}, 6)
\end{equation}

@@

The application of rewards to a block involves raising the balance of the accounts of the beneficiary address of the block and each ommer by a certain amount. We raise the block's beneficiary account by $R_{\mathrm{block}}$; for each ommer, we raise the block's beneficiary by an additional $\frac{1}{32}$ of the block reward and the beneficiary of the ommer gets rewarded depending on the block number.\hypertarget{Omega}{} Formally we define the function $\Omega$:
\begin{eqnarray}
\\ \nonumber
\Omega(B, \boldsymbol{\sigma}) & \equiv & \boldsymbol{\sigma}': \boldsymbol{\sigma}' = \boldsymbol{\sigma} \quad \text{except:} \\
\qquad\boldsymbol{\sigma}'[{\mathbf{B}_{H}}_{\mathrm{c}}]_{\mathrm{b}} & = & \boldsymbol{\sigma}[{\mathbf{B}_{H}}_{\mathrm{c}}]_{\mathrm{b}} + (1 + \frac{\lVert \mathbf{B}_{\mathbf{U}}\rVert}{32})R_{\mathrm{block}} \\
\qquad\forall_{\mathbf{U} \in \mathbf{B}_{\mathbf{U}}}: \\ \nonumber
\boldsymbol{\sigma}'[\mathbf{U}_{\mathrm{c}}] & = & \begin{cases}
\varnothing &\text{if}\ \boldsymbol{\sigma}[\mathbf{U}_{\mathrm{c}}] = \varnothing\ \wedge\ R = 0 \\
\mathbf{a}' &\text{otherwise}
\end{cases} \\
\mathbf{a}' &\equiv& (\boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathrm{n}}, \boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathrm{b}} + R, \boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathbf{s}}, \boldsymbol{\sigma}[U_{\mathrm{c}}]_{\mathrm{c}}) \\
R & \equiv & (1 + \frac{1}{8} (U_{\mathrm{i}} - {B_{H}}_{\mathrm{i}})) R_{\mathrm{block}}
\end{eqnarray}

@@

\hypertarget{block_reward_R__block}{}We define the block reward as 3 Ether:
\begin{equation}
\text{Let} \quad R_{\mathrm{block}} = 3 \times 10^{18}
\end{equation}

@@

\hypertarget{RLP_serialisation_of_a_byte_array_R__b_word_def}{}\linkdest{R__b}If the value to be serialised is a byte-array, the RLP serialisation takes one of three forms:

@@

\hypertarget{RLP_serialisation_of_a_byte_array_R__b_math_def}{}Formally, we define $R_{\mathrm{b}}$:
\begin{eqnarray}R_\{\\mathrm\{b\}\}
R_{\mathrm{b}}(\mathbf{x}) & \equiv & \begin{cases}
\mathbf{x} & \text{if} \quad \lVert \mathbf{x} \rVert = 1 \wedge \mathbf{x}[0] < 128 \\
(128 + \lVert \mathbf{x} \rVert) \cdot \mathbf{x} & \text{else if} \quad \lVert \mathbf{x} \rVert < 56 \\
\big(183 + \big\lVert \mathtt{\tiny BE}(\lVert \mathbf{x} \rVert) \big\rVert \big) \cdot \mathtt{\tiny BE}(\lVert \mathbf{x} \rVert) \cdot \mathbf{x} & \text{otherwise}
\end{cases} \\
\mathtt{\tiny BE}(x) & \equiv & (b_0, b_1, ...): b_0 \neq 0 \wedge x = \sum_{n = 0}^{n < \lVert \mathbf{b} \rVert} b_{\mathrm{n}} \cdot 256^{\lVert \mathbf{b} \rVert - 1 - n} \\
(a) \cdot (b, c) \cdot (d, e) & = & (a, b, c, d, e)
\end{eqnarray}

@@

\hypertarget{RLP_serialisation_of_a_sequence_of_other_items_R__l_word_def}{}\linkdest{R__l}If instead, the value to be serialised is a sequence of other items then the RLP serialisation takes one of two forms:
